|

### 2021-02-22 manuscript/article.Rmd
change code not working

The intervention lowered dengue incidence in `r round(as.numeric(coef(mod[[4]])[4])*100, 1)`% (CI: [`r round(tidy(mod[[4]], conf.level = 0.9, conf.int = T)$conf.low[4]*100, 1)`%, `r round(tidy(mod[[4]], conf.level = 0.9, conf.int = T)$conf.high[4]*100, 1)`%]) if we take
both treatments together and compare them with the control group. The result is
consistent around fewer weeks before and after the intervention, but it does
not reach conventional levels of statistical significance. This suggests that
the treatment effect is probably small.

>>>>

The intervention lowered dengue incidence in 10.3% (CI: [-18.9%, -1.6%]) if we take
both treatments together and compare them with the control group. The result is
consistent around fewer weeks before and after the intervention, but it does
not reach conventional levels of statistical significance. This suggests that
the treatment effect is probably small.
